\textbf{Transparency to hybrid open access through publisher-provided metadata: An article-level study of Elsevier}

### 2021-05-09 analysis/manuscript.Rmd
add journal counts to each subject in subject field  vs. oa uptake box plot

```{r oa_sub_uptake, fig.cap='Open access (OA) uptake in Elsevier hybrid journals in percent grouped by subject area and field between 2015-19. Visualized as a box-and-whiskers plot limited to an OA share of 20\\%; the red line represents the overall median (2.5), jittered dots represent individual journals. Subject fields are ordered based on the median OA uptake.', out.width="90%", fig.width=9}
p_subject <- ggplot(subject_all_years, aes(fct_reorder(description, n_oa / n, .fun = median), n_oa / n)) + 
  geom_boxplot(aes(color = subject_area)) +
  geom_jitter(alpha = .05, aes(color = subject_area), size = 1) +
  facet_wrap(~subject_area, scales = "free_y") +
  geom_hline(yintercept = median_all,  colour = "red", linetype ="dashed", size = 1) +
  scale_colour_manual(NULL, values = c("#7F3C8D", "#11A579", "#3969AC", "#F2B701"),
                      guide=FALSE) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 5L),
    expand = expansion(mult = c(0, 0.05))
  ) +
  coord_flip(ylim=c(0,0.2)) +
  labs(x = NULL, y = "Five-Year Hybrid OA Uptake Rate per Journal") +
  theme_minimal_vgrid() 
p_subject
```

>>>>

```{r oa_sub_uptake, fig.cap='Open access (OA) uptake in Elsevier hybrid journals in percent grouped by subject area and field between 2015-19. Visualized as a box-and-whiskers plot limited to an OA share of 20\\%; the red line represents the overall median (2.5), jittered dots represent individual journals. Subject fields are ordered based on the median OA uptake.', fig.asp=1.3, out.width="90%"}
# with labels
subject_all_years <- 
  inner_join(subject_all_years, subject_area_all_jn, by = "subject_area") %>%
  mutate(subject_area = glue::glue("{subject_area} ({journals_n} Journals)"))

p_subject <- ggplot(subject_all_years, aes(fct_reorder(description, n_oa / n, .fun = median), n_oa / n)) + 
  geom_boxplot(aes(color = subject_area)) +
  geom_jitter(alpha = .05, aes(color = subject_area), size = 1) +
  facet_wrap(~subject_area, scales = "free_y", nrow = 4) +
  geom_hline(yintercept = median_all,  colour = "red", linetype ="dashed", size = 1) +
  scale_colour_manual(NULL, values = c("#7F3C8D", "#11A579", "#3969AC", "#F2B701"),
                      guide=FALSE) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 5L),
    expand = expansion(mult = c(0, 0.05))
  ) +
  coord_flip(ylim=c(0,0.2)) +
  labs(x = NULL, y = "Five-Year Hybrid OA Uptake Rate\nper Journal") +
  theme_minimal_vgrid(font_size = 10) +
  theme(strip.text = element_text(face="bold"))
p_subject
```
